A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-03-29 main.tex

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth,clip]{plots/combined/time.pdf}
    \caption{Training, Prediction, and Attack times across datasets and hardware.}
    \label{fig:time}
\end{figure}

\subsection{Power}
The power consumption, illustrated in Fig.~\ref{fig:power}, tracks monetary cost (Fig.~\ref{fig:cost}) closely, probably because that's the predominant cost for the datacenter itself~\cite{dayarathna2015data}, so it is unsurprising that cloud billing is colinear with this metric. Furthermore, we see that the largest dataset (CIFAR100) and smallest GPU (L4) require the least amount of power (Fig.~\ref{fig:power}).

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth,clip]{plots/combined/power.pdf}
    \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
    \label{fig:power}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth,clip]{plots/combined/cost.pdf}
    \caption{Training, Prediction, and Attack Monetary Cost Across Datasets and Hardware}
    \label{fig:cost}
\end{figure}

>>>>

\begin{figure*}[h]
    \centering
    \includegraphics[width=.7\textwidth,clip]{plots/combined/time.pdf}
    \caption{Training, Prediction, and Attack times across datasets and hardware.}
    \label{fig:time}
\end{figure*}

\subsection{Power}
The power consumption during training, inference, and attack generation for all hardware and datasets is illustrated in Fig.~\ref{fig:power}. It is clearly obvious that training is several orders of m

It tracks monetary cost (Fig.~\ref{fig:cost}) closely, probably because that's the predominant cost for the datacenter itself~\cite{dayarathna2015data}, so it is unsurprising that cloud billing is colinear with this metric. Furthermore, we see that the largest dataset (CIFAR100) and smallest GPU (L4) require the least amount of power (Fig.~\ref{fig:power}).

\begin{figure*}[h]
    \centering
    \includegraphics[width=0.7\textwidth,clip]{plots/combined/power.pdf}
    \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
    \label{fig:power}
\end{figure*}

@@

\begin{figure*}
    \centering
    \caption{Training, Prediction, and Attack Monetary Cost Across Datasets and Hardware}
    \label{fig:cost}
\end{figure*}
